---
title: "Public data results — bucketed regressions"
format: html
execute:
  warning: false
  message: false
type: source
---

```{r setup}
rm(list = ls())
source("tracks/first-draft-may2026/code/common_first_draft.R")
cl <- ~ RSSDID + zip5
```

```{r load}
master_parts <- Sys.glob(file.path(data_dir, "master_bank_zip_year_*_part*.rds"))
dates        <- regmatches(master_parts, regexpr("\\d{8}", master_parts))
latest_date  <- max(dates)
master_parts <- sort(master_parts[dates == latest_date])
bc_path      <- load_latest(file.path(data_dir, "bank_cycle_first_stage_*.rds"))

dt <- rbindlist(lapply(master_parts, readRDS))
bc <- setDT(readRDS(bc_path))
```

```{r prep}
setorder(dt, RSSDID, zip5, yr)
dt[, n_branches_lag1    := shift(n_branches_bzt,    1L), by = .(RSSDID, zip5)]
dt[, bank_in_state_lag1 := shift(bank_in_state_bzt, 1L), by = .(RSSDID, zip5)]
dt[, share_bzt_lag1     := shift(share_bzt,         1L), by = .(RSSDID, zip5)]
dt[, opening := as.integer(n_branches_bzt > n_branches_lag1)]

dt[, n_large_banks_zip      := sum(n_branches_bzt > 0L), by = .(yr, zip5)]
dt[, n_large_banks_zip_lag1 := shift(n_large_banks_zip, 1L), by = .(RSSDID, zip5)]

dt[, g_dep_zip_t1_t3 := log1p(dep_zip_total_lag1) - log1p(dep_zip_total_lag3)]
dt[, g_hmda_t1_t3    := log1p(hmda_amt_lag1)      - log1p(hmda_amt_lag3)]
dt[, g_cra_t1_t3     := log1p(cra_amt_lag1)       - log1p(cra_amt_lag3)]
dt[, log_dep_zip_lag1    := log1p(dep_zip_total_lag1)]
dt[, log_avg_agi_lag1    := log(avg_agi_lag1)]
dt[, log_n_branches_lag1 := log1p(n_branches_lag1)]
dt[, hhi_lag1            := deposit_hhi_zip_lag1 / 10000]
dt[is.na(share_bzt_lag1), share_bzt_lag1 := 0]

dt[!is.na(int_exp_assets_share_undercut),
   high_IEA := as.integer(int_exp_assets_share_undercut > 0.5)]
dt[!is.na(rate_paying_adv),
   high_rate_paying := as.integer(rate_paying_adv > 0)]

dt[, size_bucket := assign_bucket(bank_assets)]
bc[, size_bucket := assign_bucket(bank_assets * 1000)]
```

```{r filter}
ar_master <- dt[
  yr <= 2024L                        &
  !is.na(size_bucket)                &
  !is.na(n_branches_lag1)            &
  !is.na(bank_in_state_lag1)         &
  !is.na(n_large_banks_zip_lag1)     &
  !is.na(g_dep_zip_t1_t3)            &
  !is.na(g_hmda_t1_t3)               &
  !is.na(g_cra_t1_t3)                &
  !is.na(log_dep_zip_lag1)           &
  !is.na(log_avg_agi_lag1)           &
  !is.na(log_pop_density_lag1)       &
  !is.na(median_age_lag1)            &
  !is.na(pct_college_educated_lag1)  &
  !is.na(hhi_lag1)                   &
  !is.na(no_bank_zip_lag1)            
]
```

```{r buckets}
d_big <- copy(ar_master[size_bucket == "ge_100bn"])
d_mid <- copy(ar_master[size_bucket == "10_100bn"])
d_sml <- copy(ar_master[size_bucket == "1_10bn"])

d_big[, g_dep_zip_t1_t3           := winsor(g_dep_zip_t1_t3),           by = yr]
d_big[, g_hmda_t1_t3              := winsor(g_hmda_t1_t3),              by = yr]
d_big[, g_cra_t1_t3               := winsor(g_cra_t1_t3),               by = yr]
d_big[, median_age_lag1           := winsor(median_age_lag1),           by = yr]
d_big[, pct_college_educated_lag1 := winsor(pct_college_educated_lag1), by = yr]

d_mid[, g_dep_zip_t1_t3           := winsor(g_dep_zip_t1_t3),           by = yr]
d_mid[, g_hmda_t1_t3              := winsor(g_hmda_t1_t3),              by = yr]
d_mid[, g_cra_t1_t3               := winsor(g_cra_t1_t3),               by = yr]
d_mid[, median_age_lag1           := winsor(median_age_lag1),           by = yr]
d_mid[, pct_college_educated_lag1 := winsor(pct_college_educated_lag1), by = yr]

d_sml[, g_dep_zip_t1_t3           := winsor(g_dep_zip_t1_t3),           by = yr]
d_sml[, g_hmda_t1_t3              := winsor(g_hmda_t1_t3),              by = yr]
d_sml[, g_cra_t1_t3               := winsor(g_cra_t1_t3),               by = yr]
d_sml[, median_age_lag1           := winsor(median_age_lag1),           by = yr]
d_sml[, pct_college_educated_lag1 := winsor(pct_college_educated_lag1), by = yr]
```

```{r macros}
setFixest_fml(
  ..fc = as.formula(paste("~", base_rhs)),
  ..fe = ~ RSSDID^yr + state_fips^yr
)
```


## Deposit beta — first stage (bank-cycle data)

```{r fs-fmls}
fml_full <- deposit_exp_chg ~ factor_age_bin + dividend_frac + college_frac +
  log(family_income) + bank_hhi + log(bank_assets) + population_density +
  trans_accts_frac_assets + uninsured_deposits_frac + time_deposits_assets

fml_soph <- deposit_exp_chg ~ sophisticated_frac + factor_age_bin +
  log(family_income) + bank_hhi + log(bank_assets) + population_density +
  trans_accts_frac_assets + uninsured_deposits_frac + time_deposits_assets
```

```{r fs-pooled}
fs_e_full <- feols(fml_full, bc[cycle == "cycle_0406"], notes = FALSE)
fs_m_full <- feols(fml_full, bc[cycle == "cycle_1619"], notes = FALSE)
fs_l_full <- feols(fml_full, bc[cycle == "cycle_2224"], notes = FALSE)
fs_e_soph <- feols(fml_soph, bc[cycle == "cycle_0406"], notes = FALSE)
fs_m_soph <- feols(fml_soph, bc[cycle == "cycle_1619"], notes = FALSE)
fs_l_soph <- feols(fml_soph, bc[cycle == "cycle_2224"], notes = FALSE)
etable(fs_e_full, fs_m_full, fs_l_full,
       fs_e_soph, fs_m_soph, fs_l_soph,
       headers = c("Early-F","Mid-F","Late-F","Early-S","Mid-S","Late-S"))
```

## Deposit beta — main regression

```{r beta-subsets}
d_big_b <- d_big[!is.na(deposit_beta) & is.finite(deposit_beta)]
d_mid_b <- d_mid[!is.na(deposit_beta) & is.finite(deposit_beta)]
d_sml_b <- d_sml[!is.na(deposit_beta) & is.finite(deposit_beta)]
d_big_b[, deposit_beta := winsor(deposit_beta), by = yr]
d_mid_b[, deposit_beta := winsor(deposit_beta), by = yr]
d_sml_b[, deposit_beta := winsor(deposit_beta), by = yr]
```

```{r beta-main}
m_beta_big <- feols(opening ~ deposit_beta + ..fc | ..fe, d_big_b, cluster = cl)
m_beta_mid <- feols(opening ~ deposit_beta + ..fc | ..fe, d_mid_b, cluster = cl)
m_beta_sml <- feols(opening ~ deposit_beta + ..fc | ..fe, d_sml_b, cluster = cl)
etable(m_beta_big, m_beta_mid, m_beta_sml, headers = c(">=$100B","$10B-$100B","$1B-$10B"))
```

## Rate-paying capacity over incumbents

The economic channel: a focal bank with lower non-interest costs has slack to pay higher deposit rates without compressing margins, so it is more likely to enter (and win deposits in) zips dominated by less-efficient incumbents. Two complementary proxies, both built bank-zip-year:

**(1) Cost-side proxy — `rate_paying_adv` (indirect).** From FFIEC Q4 Call Reports, define each bank-year's efficiency ratio as `eff_ratio = nonint_exp / (int_inc_net + nonint_inc)` (lower = leaner cost structure), winsorized 1/99 within year. For each zip-year, build a **deposit-weighted incumbent benchmark** of `eff_ratio` across all SOD branches in that zip, excluding the focal bank's own deposits and own eff_ratio. Then

`rate_paying_adv = incumb_eff_excl - focal_eff_ratio`

evaluated at the focal bank's `t-1` eff_ratio (predetermined relative to the opening decision), winsorized 1/99 within year. Positive ⇒ focal is **leaner** than the local incumbent mix ⇒ has cost slack to outbid on deposit rates. `high_rate_paying = 1{rate_paying_adv > 0}` is the discrete version.

**(2) Direct rate proxy — `int_exp_assets_share_undercut` / `high_IEA`.** Use focal bank's `int_exp_total / total_assets` (≈ deposit rate paid) at `t-1`, and compute the deposit share of zip incumbents whose `int_exp_assets` is **below** the focal's. `high_IEA = 1{share > 0.5}` ⇒ focal already pays a higher rate than the majority of incumbent deposits in the zip.

Construction: `tracks/first-draft-may2026/code/sample-construction/02_build_bank_advantage.R`.

```{r rp-subsets}
d_big_e <- d_big[!is.na(rate_paying_adv) & is.finite(rate_paying_adv)]
d_mid_e <- d_mid[!is.na(rate_paying_adv) & is.finite(rate_paying_adv)]
d_sml_e <- d_sml[!is.na(rate_paying_adv) & is.finite(rate_paying_adv)]
d_big_e[, rate_paying_adv := winsor(rate_paying_adv), by = yr]
d_mid_e[, rate_paying_adv := winsor(rate_paying_adv), by = yr]
d_sml_e[, rate_paying_adv := winsor(rate_paying_adv), by = yr]

d_big_i <- d_big[!is.na(high_IEA)]
d_mid_i <- d_mid[!is.na(high_IEA)]
d_sml_i <- d_sml[!is.na(high_IEA)]
```

```{r rp-combined}
m_rp_big  <- feols(opening ~ deposit_beta + rate_paying_adv + ..fc | ..fe, d_big_e, cluster = cl)
m_iea_big <- feols(opening ~ deposit_beta + high_IEA        + ..fc | ..fe, d_big_i, cluster = cl)
m_rp_mid  <- feols(opening ~ deposit_beta + rate_paying_adv + ..fc | ..fe, d_mid_e, cluster = cl)
m_iea_mid <- feols(opening ~ deposit_beta + high_IEA        + ..fc | ..fe, d_mid_i, cluster = cl)
m_rp_sml  <- feols(opening ~ deposit_beta + rate_paying_adv + ..fc | ..fe, d_sml_e, cluster = cl)
m_iea_sml <- feols(opening ~ deposit_beta + high_IEA        + ..fc | ..fe, d_sml_i, cluster = cl)
etable(m_rp_big, m_iea_big, m_rp_mid, m_iea_mid, m_rp_sml, m_iea_sml,
       headers = c(">=$100B (rp)", ">=$100B (iea)",
                   "$10B-$100B (rp)", "$10B-$100B (iea)",
                   "$1B-$10B (rp)", "$1B-$10B (iea)"))
```

## Combined: deposit_beta + rate_paying_adv

```{r comb-subsets}
d_big_c <- d_big[!is.na(rate_paying_adv) & is.finite(rate_paying_adv) &
                 !is.na(high_IEA) &
                 !is.na(deposit_beta) & is.finite(deposit_beta)]
d_mid_c <- d_mid[!is.na(rate_paying_adv) & is.finite(rate_paying_adv) &
                 !is.na(high_IEA) &
                 !is.na(deposit_beta) & is.finite(deposit_beta)]
d_sml_c <- d_sml[!is.na(rate_paying_adv) & is.finite(rate_paying_adv) &
                 !is.na(high_IEA) &
                 !is.na(deposit_beta) & is.finite(deposit_beta)]
d_big_c[, rate_paying_adv := winsor(rate_paying_adv), by = yr]
d_mid_c[, rate_paying_adv := winsor(rate_paying_adv), by = yr]
d_sml_c[, rate_paying_adv := winsor(rate_paying_adv), by = yr]
d_big_c[, deposit_beta   := winsor(deposit_beta),   by = yr]
d_mid_c[, deposit_beta   := winsor(deposit_beta),   by = yr]
d_sml_c[, deposit_beta   := winsor(deposit_beta),   by = yr]
d_big_c[, high_rate_paying := as.integer(rate_paying_adv > 0)]
d_mid_c[, high_rate_paying := as.integer(rate_paying_adv > 0)]
d_sml_c[, high_rate_paying := as.integer(rate_paying_adv > 0)]
```

```{r combd}
m09_rp_big  <- feols(opening ~ deposit_beta * high_rate_paying + ..fc | ..fe, d_big_c, cluster = cl)
m09_iea_big <- feols(opening ~ deposit_beta * high_IEA         + ..fc | ..fe, d_big_c, cluster = cl)
m09_rp_mid  <- feols(opening ~ deposit_beta * high_rate_paying + ..fc | ..fe, d_mid_c, cluster = cl)
m09_iea_mid <- feols(opening ~ deposit_beta * high_IEA         + ..fc | ..fe, d_mid_c, cluster = cl)
m09_rp_sml  <- feols(opening ~ deposit_beta * high_rate_paying + ..fc | ..fe, d_sml_c, cluster = cl)
m09_iea_sml <- feols(opening ~ deposit_beta * high_IEA         + ..fc | ..fe, d_sml_c, cluster = cl)
etable(m09_rp_big, m09_iea_big, m09_rp_mid, m09_iea_mid, m09_rp_sml, m09_iea_sml,
       headers = c(">=$100B (rp)", ">=$100B (iea)",
                   "$10B-$100B (rp)", "$10B-$100B (iea)",
                   "$1B-$10B (rp)", "$1B-$10B (iea)"))
```

## Cross-sell: deposit_beta x (mortgage_presence + cra_presence)

```{r cs-add}
m_cs_a_mort_big <- feols(opening ~ deposit_beta + mortgage_presence + ..fc | ..fe, d_big_b, cluster = cl)
m_cs_a_cra_big  <- feols(opening ~ deposit_beta + cra_presence      + ..fc | ..fe, d_big_b, cluster = cl)
m_cs_a_mort_mid <- feols(opening ~ deposit_beta + mortgage_presence + ..fc | ..fe, d_mid_b, cluster = cl)
m_cs_a_cra_mid  <- feols(opening ~ deposit_beta + cra_presence      + ..fc | ..fe, d_mid_b, cluster = cl)
m_cs_a_mort_sml <- feols(opening ~ deposit_beta + mortgage_presence + ..fc | ..fe, d_sml_b, cluster = cl)
m_cs_a_cra_sml  <- feols(opening ~ deposit_beta + cra_presence      + ..fc | ..fe, d_sml_b, cluster = cl)
etable(m_cs_a_mort_big, m_cs_a_cra_big, m_cs_a_mort_mid, m_cs_a_cra_mid, m_cs_a_mort_sml, m_cs_a_cra_sml,
       headers = c(">=$100B (mort)", ">=$100B (cra)",
                   "$10B-$100B (mort)", "$10B-$100B (cra)",
                   "$1B-$10B (mort)", "$1B-$10B (cra)"))
```

```{r cs-int}
m_cs_i_mort_big <- feols(opening ~ deposit_beta * mortgage_presence + ..fc | ..fe, d_big_b, cluster = cl)
m_cs_i_cra_big  <- feols(opening ~ deposit_beta * cra_presence      + ..fc | ..fe, d_big_b, cluster = cl)
m_cs_i_mort_mid <- feols(opening ~ deposit_beta * mortgage_presence + ..fc | ..fe, d_mid_b, cluster = cl)
m_cs_i_cra_mid  <- feols(opening ~ deposit_beta * cra_presence      + ..fc | ..fe, d_mid_b, cluster = cl)
m_cs_i_mort_sml <- feols(opening ~ deposit_beta * mortgage_presence + ..fc | ..fe, d_sml_b, cluster = cl)
m_cs_i_cra_sml  <- feols(opening ~ deposit_beta * cra_presence      + ..fc | ..fe, d_sml_b, cluster = cl)
etable(m_cs_i_mort_big, m_cs_i_cra_big, m_cs_i_mort_mid, m_cs_i_cra_mid, m_cs_i_mort_sml, m_cs_i_cra_sml,
       headers = c(">=$100B (mort)", ">=$100B (cra)",
                   "$10B-$100B (mort)", "$10B-$100B (cra)",
                   "$1B-$10B (mort)", "$1B-$10B (cra)"))
```
